\begin{alltt}\normalfont\textbf{75000_Tokkul}: \emph{Compromise happened with ACA already.

This is hostage taking.

EDIT:

Aw look he deleted his post so he wouldn't have to face facts.}

\textbf{None}: \emph{[deleted]}

\textbf{pyrodinium}: \emph{No you don't understand the ACA was already talked over in 2010 with it passing the house. The republicans want to back track and basically want to devote for something they already approved. Thats like taking a loan from a bank and then when it comes time to pay the interest you decide to shut down the bank because you no longer like the terms you agreed too.}

\textbf{None}: \emph{[deleted]}

\textbf{ArthurLaumann}: \emph{"No one "negotiates" over laws that have already passed"

Really? Then why isn't the Volstead Act still the law of the land?

"America is a democracy"

America is a Republic.

Don't you ever get tired of being wrong?}

\textbf{pyrodinium}: \emph{None, but thats how democracy works the republicans voted and they didn't have enough to prevent it passing as the final vote was 220 for, 211 against. They lost, they had their chance to negotiate and didn't want to but then waited until the last minute to shutdown the government three years after it passed. The house passes bills as a single entity and the house passed it in 2010, passed the senate, signed by the president. Only now did they want to come back to the table to "negotiate."}

\textbf{None}: \emph{[deleted]}

\textbf{pyrodinium}: \emph{Because those tax cuts were set to expire in ten years and republicans wanted to extend it farther. Also stop deleting your comments it makes you look childish.}

\textbf{None}: \emph{[deleted]}

\textbf{pyrodinium}: \emph{And yet here you are deleting everything you post because your afraid of being criticized. At least I stand by my comments}

\textbf{pyrodinium}: \emph{\textgreater Listen, dude, if you go negative karma in a subreddit you get put on a 9 minute throttle and that's annoying. Thanks for the instant downvote, by the way.
I deleted it after you replied so I knew you had seen it. Did you want me to leave it up so someone else could hold your hand through a difficult discussion? Think for yourself, for once. Relying on talking points designed for simpletons and other idiots in your hate filled political tribe to backfill your lack of critical thought isn't a recipe for success.



Well Beberebozo since you seem to think the comment section is a private message box I could see how you wanted this conversation to remain private but bad news for you is this a thread based commenting system and if you can't learn to deal with multiple people then maybe you shouldn't comment expecting that no one else would even look into what your saying as well. The whole point of the comment section is for multiple people to see what you say and exchange views and if you are unwilling to do that then the comment section probably isn't for you.}

\textbf{sluggdiddy}: \emph{You again huh? How many times do your bullshit talking points have to be refuted before you change your views? Is therw any amount of evidence that could change your mind or are you operating based off of pure idealogy ? }

\textbf{ArthurLaumann}: \emph{Bother with what?}

\textbf{armauld}: \emph{You probably don't remember but we used to chat regularly.  I would chat/debate with many of the right-wingers haunting /r/politics and I sincerely tried to do it politely and respectfully.

I gave up because, when I did try to discuss things calmly and logically. They turned to insults or getting all worked up.

So I quit trying. 
}

\textbf{angiers}: \emph{There are proper procedures to redact laws. Shutting down all of government is not one of them.}

\textbf{ArthurLaumann}: \emph{Translation: I got beat so I accuse others of being mean then I ran away.}

\textbf{armauld}: \emph{What?  Please, where did I say anything that even hinted at that?  With you, you changed your name and ran away.  

Besides, I've had a few draws in my day but nobody beats me, baby.}

\textbf{ArthurLaumann}: \emph{What does the GOP have left when Obama, Reid &amp; Pelosi won't bargain in good faith. Our Constitution rightly grants the Speaker the power to keep an obstinate chief executive from becoming an oligarch and Boehner is exercising that right.}

\textbf{ArthurLaumann}: \emph{"you changed your name and ran away"

Wrong. You lose (again, baby).

Banned by liberal mods who can't fathom conservative thought on r/politics.}

\textbf{falor42}: \emph{Wow, your disconnect from reality is intense...}

\textbf{Semyonov}: \emph{\textgreater  won't bargain in good faith.

Oh, you mean like the good House Majority Leader and Speaker of the House, Eric Cantor and John Boehner (respectively) have been bargaining in good faith?

You know, like not passing a rule change that disallows anyone but the Speaker of the House from proposing the re-opening of the government? Like that good faith?

Please. }

\textbf{adaminator1}: \emph{And that, my friends, was a slapdown.}

\textbf{Semyonov}: \emph{Are you sure? I wouldn't particularly put it past them. Intelligent people are not only found in the US, but also in caves too.}

\textbf{rythmik1}: \emph{Pear Farty.}

\textbf{WizardHatchet}: \emph{\textgreater Why aren't the the members of the tea party looked at as egoistic scum by the public in USA?

Is this is a good place to ask? Any comment here with a good opinion of them would be downvoted, so you are unlikely to get a good picture of what the average American thinks of them.}

\textbf{Holos620}: \emph{Corruption Party}

\textbf{alexander1701}: \emph{No, I'm just here to make fun of the source.

Though really I think the American People are to blame. The electorate should really be stepping in before Solomon's proverbial baby is cut in two, and pledging to never again vote for any sitting member of congress if a resolution isn't reached.}

\textbf{bravestmistake}: \emph{The electorate has no means of controlling our elected officials after elections. There's the drawback in the system. Possibly if we had a way to get signatures to recall elected officials in the House this may be possible but until that time comes, we can't do anything. (I do not have any knowledge of if that is possible so if it is, I welcome the information).}

\textbf{DevonWeeks}: \emph{There's also some Senate Democrats that need to be recalled that are deliberately unhelpful to the process.  If you think the need for a recall is limited to the House, you're wrong. }

\textbf{gribbly}: \emph{Because there's no single "public" in the America. You're talking about 350 million people. They don't all think the same thing.

Certainly the Tea Party doesn't poll well.}

\textbf{AllHeilSLAYER}: \emph{Koch Party.}

\textbf{napalm_beach}: \emph{I suspect OP needs to know even a bit more than that. }

\textbf{will_holmes}: \emph{Well, in most parliamentary systems, failing to pass a budget effectively means that a government has collapsed or has failed to form, and an immediate reelection is triggered. The American People really have a right to be consulted at this point, as far as the common schools of thought around democratic governance goes.}

\textbf{napalm_beach}: \emph{Dude, you want to call the shots you have to win the votes.  That's what your sacred constitution stipulates.  The minority opposition may have the ability to stop legislation, thereby giving them negotiating power. But you don't do it with brinksmanship like this.

Personally, at this point I honk default is inevitable.  It's going to be a cluster fuck and your party is going to be destroyed.  Which is a bummer, because we need two sane parties.

EDIT:  you're to your.  ack.}

\textbf{Saw_a_4ftBeaver}: \emph{[Lemonparty.com](http://www.lemonparty.com)}

\textbf{bravestmistake}: \emph{I have no problem with the Senate process at the moment (minus the current use of filibusters but that's a different story for a different time) and that's fine if you believe that some should be recalled but the whole government is at a standstill due to 1 person who won't bring up a vote on a clean CR. There's no current fear of reprisal that any constituents can engage in and that's the problem, we apparently don't own our representatives like we should. They should be beholden to their own citizens at all times, not once every 2 years/6 years.}

\textbf{None}: \emph{\textgreater ...we apparently don't own our representatives like we should. 

Except, this entire thing is happening because Tea Party Republicans don't want to get killed in the midterms in 2014.}

\textbf{thistlefink}: \emph{Inaccurate,

This is happening because the non-TP Republicans don't want to get swamped by more "grassroots" money bombs by the Koch brothers.}

\textbf{DevonWeeks}: \emph{I get what you're saying, but that claim that a clean CR would pass isn't even true.  It was empty claim made by one Senator that he thought he had the votes, but every Republican asked about said they aren't one of those 17.  It would be different if there was substance to the claim, but there never was.  Also, Harry Reid has refused to allow many, many things to be voted on in the Senate.  I have no sympathy for him now that he's on the receiving end of the same tactic.  I don't like that tactic, don't get me wrong.  But, I just don't give a flip about Reid's nonsense and think it's good he's getting to swap sides here.  }

\textbf{None}: \emph{I'm sorry, I pretty much regard any explanation that relies on the Koch Brothers as an explanation for all our woes to be pretty devoid of factual evidence.  There are voters who's interests do not align with yours.  They want Republicans in Congress to represent them, and if they fail to, those voters will vote them out of the primaries.

Sure, the Koch Brothers are definitely bankrolling political groups that side with them.  So is George Soros.  His influence in politics goes strangely ignored in this subreddit.}

\textbf{alexander1701}: \emph{Congressional democracies are designed differently on purpose. They're meant to allow for minority dissent if the minority in question feels strongly enough (right or wrong).

The system is working as intended, it's the electorate that is not. Big money has allowed odd opinions to rule.}

\textbf{HamBiscuit}: \emph{Correction: the idiots pulling this crap are Fiscal Conservatives, NOT Social Conservatives.  Social Conservatives, or religious extremists as you call them, put all their legislative energies into attacking reproductive rights and undermining Roe v Wade.

Fiscal Conservatives, or Tea Party loons, get their money and inspiration from the Libertarian Koch Brothers, Ayn Rand, and, yes, the Austrian School of Economics.  They also get their inspiration from the weasel who helped usher in their political tactics, the Godfather of political/fiscal stupidity...Newt Gingrich.}

\textbf{dcux}: \emph{\textgreater  bankrolling political groups that side with them.

That's one way to put it.
}

\textbf{ademnus}: \emph{Absolutely I do. The day after 9/11, republicans went into takeover overdrive. I trace their influence right back to 9/11.}

\textbf{zap2}: \emph{I'm not going to commit to voting against my Congressman because some people there are terrible.

For the record, my Congressman is an ex-NFL player who is a member of the GOP. I voted against him last election. I disagree with him on almost everything he ran on.

But he's one of the GOP members in the House who has publicly said "Let's end the shut down, bring it up for a vote" I'm not sure if I'll vote for him in 2014, but if I don't, it not because of the shut down. He's handling that pretty well.}

\textbf{pheonixvl}: \emph{There is nothing fiscally conservative about defaulting on your debts.}

\textbf{msdrahcir}: \emph{A majority the house supports passing the bill that would extend government funding until  further down the road (I believe January). This claim is not empty, the record on this is solid.}

\textbf{None}: \emph{I believe they are both fiscal and social conservatives. }

\textbf{lexsird}: \emph{\textgreater  but it's pretty obvious what people mean when they complain about the Reddit Echo Chamber. 

Yeah, because Reddit is to blame. }

\textbf{lexsird}: \emph{\textgreater  so you are unlikely to get a good picture of what the average American thinks of them.

Wow, that's pretty out there don't you think? Nice attempt to marginalize critics and come up with some fictional "average" American who supports your opinion. 

This is what we have to deal with and the clock is running out. Thursday, we got until then. That genie isn't going back in the bottle. 

}

\textbf{DevonWeeks}: \emph{Says one who cites no evidence. }

\textbf{MarinTaranu}: \emph{Only a meathead will respond to force with the same kind of force. Smart people understand asymmetric warfare where you use your advantages wisely, concentrate against an enemy's weak points, fight in depth and use the element of surprise. }

\textbf{msdrahcir}: \emph{your objection to the source referenced by DarkKobold?}

\textbf{nevereon}: \emph{Oh come on. I'm probably more left than most of reddit and even I have to admit that there is an insane bias on this site. Let's be real guys.}

\textbf{MarinTaranu}: \emph{Your solution is retarded. Most representatives want a vote on the issue. Sessions mucked up the rules that only the Speaker Boehner can bring the bill on the floor for a vote.}

\textbf{DevonWeeks}: \emph{The fact that it cites mostly quotes from 9/29, before the most recent developments and rhetoric.  Plus, several of those comments are out of context and have been refuted by the very people who quoted them as not being unconditional support for a clean CR.  But, it's HuffPo.  What else could one expect?  When CNN reported the same story, they said...

\textgreater  As is the case with all vote counts, the numbers continually evolve and change by the hour and day.

Since then, some of the very people on that list are the ones who proposed bills with conditions attached to them!  Plus, daring the speaker to call a vote on something?   Where have I heard that?  Oh, yeah!  The Senate... for years.}

\textbf{lexsird}: \emph{Oh really? Check out this nugget comment I just stumbled across examining the dialog across the Internet. 

-------------------

***MSNBC OBAMA BOOT LICKER NETWORK BREAKING NEWS ALERT***

"This is Chris Matthews, POTUS bunghole-sniffer-in-chief, and it looks like President Obama has activated the FSA!"

"I've hoped &amp; prayed that the greatest president, leader &amp; person in all of history would start playing hardball, and it looks like he heard my advice."

"Now, let's go over to our fellow cable news network &amp; Obama testicle washer &amp; scrubber, CNN, where Wolf Blitzer is in The Situation Room with the latest news on how it's unreasonable to NOT raise the debt ceiling without any conditions, unlike the time when Obama voted AGAINST raising the debt ceiling when the national debt was less than half the amount it is now."

***THIS HAS BEEN A MSNBC OBAMA BOOT LICKER NETWORK BREAKING NEWS ALERT***

-------------------

There we have it, a copy/paste and we see what bias looks like outside of our relatively quiet and rational environment. I know it's disgusting and repulsive, but I suggest you take a walk around the Internet and gauge this. I know this example is vulgar and I wouldn't blame the mods for shooting my post down, but it's fresh and relative to the mindset we are dealing with. }

\textbf{BubbaRobinson}: \emph{I lived in the Bay Area as well and the slap on the face inequality there coupled with shit-eating grins plastered on every person was too much for me.

Libertarians deserve a special place in hell. If you were provided for, more than you provided to humanity, you deserve a special place in hell.}

\textbf{WizardHatchet}: \emph{\textgreater  and come up with some fictional "average" American who supports your opinion.

The country is close to 50:50 republican:democrat, with democrats a bit higher by population. The number of Tea Partiers is smaller, but still a lot of higher than your average /r/politics sample. 

I used the word "average"-- the average American would actually lean slightly in favor of Democrats, or least we could say they are close to the center. But the average would also not hate the Tea Party nearly as much as people here, which is relevant to the question "why don't Americans dislike them?".
}

\textbf{lexsird}: \emph{People in this country are very apathetic to politics. They are super slow on the uptake of political events and they have oceans of propaganda to swim through. 

It takes an event of a certain magnitude to involve them. Here we have it. I'm pretty confident as the facts are presented, in spite of screaming shills, people will figure it out. }

\textbf{The_Drizzle_Returns}: \emph{Case and point can be found in this exact thread. 

\textgreater  The Tea Party was and is based on the belief that the Federal Government has a role set forth in the Constitution and should be limited to that role because doing all these other things threatens our country's survival and by survival I mean the real survival not you're being able to buy a cheeseburger for $1.00 at McD. That doesn't sound like scum to me.

[Downvoted -26](http://www.reddit.com/r/politics/comments/1oij25/tea_party_republicans_in_the_house_of/ccsclal). I don't agree with what he is saying but according to the rules of this subreddit he should not be downvoted (in fact a case could be made that he should upvoted for quality of content by providing a response to the question asked). If you wouldn't report the comment, you shouldn't down vote it. }

\textbf{nived321}: \emph{Im glad i got a passport}

\textbf{HamBiscuit}: \emph{Tell that to the Tea Party whose battle cry is "Cut federal spending".  I didn't say it was rational, but it is what it is.}

\textbf{HamBiscuit}: \emph{They wear both hats at times, but fiscal conservatism is their guiding light and they openly admit as much.

The true agenda at the heart of their actions is killing The Affordable Care Act, Social Security and Medicare.  They won't come out and openly admit their designs on the second two items, but it's clear by their actions.  This is fiscal cutthroat 101.

Social Conservatives are merely the political pawns used to get Fiscal Conservatives the political power they can't gain on their own.  How many Republicans have you seen run for office with killing Social Security and Medicare as their campaign platform?}

\textbf{UVladBro}: \emph{Yup, lived in the Bay Area for a huge chunk of my life and dealt with the extreme conservatives in Inland California (San Joaquin county). 

The amount of self-centered egotism is remarkable. I can attempt to try to understand the viewpoint of people who are selfish and would rather see everyone else suffer than to inconvenience themselves but there is a different type of person I just can't understand. 

The people that go out of their way to purposely put others in suffering, a lot of times to gain no real tangible benefit, are just unbelievable.}

\textbf{OTSProspect}: \emph{I completely agree with dismantling Obama care, Medicare, and social security.}

\textbf{BubbaRobinson}: \emph{bro fist bump}

\textbf{HamBiscuit}: \emph{You're entitled to your opinion, but you're wrong to advocate it in this country.  

You may not need those programs now, but if your wishes come true, you will age and when you finally recognize the insanity you're spouting it will be too late.  The elderly suffered mightily in this country before Social Security and Medicare showed up.  Repealing those programs will only restore that poverty and suffering.

If you think you'll be immune from it, you won't be.  Even if you get lucky and become wealthy, you 'll have a hard time finding a decent medical facility because most of them will go under from the position you're advocating.}

\textbf{BashCo}: \emph{The users of Reddit are certainly to blame for the wife's reputation as an echo chamber. }

\textbf{root66}: \emph{Fucking Vice... We only need one of The Onion. This isn't even witty or well-written.}

\textbf{onemanlegion}: \emph{Down voting = disagree

Upvoting = agree}

\textbf{timmytimtimshabadu}: \emph{Oops yeah! Mensheviks were the larger group, but lenins Bolsheviks were the minority, and orchestrated the coup. They called themselves the majority. That's what it was, thanks!}

\textbf{Nameless_Archon}: \emph{I'm thinking the wife's reputation as an echo chamber is due to not being able to close her legs.

Wait - what were we talking about again?}

\textbf{ArthurLaumann}: \emph{We have the votes, thanks to the Constitution. The House has 234 Republicans and 201 Democrat party members.}

\textbf{napalm_beach}: \emph{No, you have 234 Republicans, that does not mean you have the votes.  No one will know that until the house votes and proves it either way.}

\textbf{The_Drizzle_Returns}: \emph{The rules say explicitly not to do that.....}

\textbf{ArthurLaumann}: \emph{234 is the majority needed to set the rules, as they've legally done. Same when Pelosi held the Speakership.}

\textbf{napalm_beach}: \emph{Yes, except they didn't vote on the rule change, it was done in committee.

But it doesn't matter now anyway, it appears you guys didn't have the votes after all.  Your party is lucky.}

\textbf{ArthurLaumann}: \emph{Legally done in committee. 

The American people lost in this vote. The national debt is $17T, up almost $7T since Obama took office. Without fiscal sanity, it will continue to go up.}

\textbf{napalm_beach}: \emph{Fiscal sanity is coming back, at a modest pace, as it should.  The deficit is back to 30 year average levels and going lower yet.  Your party has done well in that regard and the public will is behind further reduction.  It will come.

That's to be commended, but not the shutdown.  This was expensive, unnecessary bullshit that only further damaged your party's brand.}

\textbf{ArthurLaumann}: \emph{I commend you for admitting that debt &amp; deficits are important. Most liberals on Reddit deny it's an issue and won't decry runaway spending. If only more of the Democrat party members in Congress felt the way you do.}

\textbf{inoffensive1}: \emph{I never accused you of not debating the issue.  My problem was where you felt the need to drop in on *this* discussion specifically not to debate, but to lash out irrationally (at bias, remember, not reposts.  Reposts didn't come to your argument till later.)}

\textbf{DevonWeeks}: \emph{And?  You're the one who decided to try and refute my "bias bash" by calling the link news, and then when I said it wasn't news, you tried to say it wasn't news but politics.  Maybe you need to go back and read the flow of this conversation.  

It started with me calling this source biased, sarcastically.  Then, you started in with how biased "news" was just a fact of life to be dealt with (something I don't disagree on).  Then, when I pointed out that this was Obama's own website (or, more accurately, OFA) and not even a news article, you proceeded to say it didn't matter because it was politics.  I then proceeded to explain that the website in this post and all its contents are already being discuss at length in many other threads and that citing a mouthpiece for a politician doesn't further discussion.  I then offered an equally meritorious post in the form of John Boehner's response to Obama, which you then decided would be unhelpful despite being no different in principle from this one.

You haven't made a lick of sense and certainly lack any continuity in the contents of your posts.  If you really want people to "add to the discussion" and feel links like this do so, then the direct to Boehner's website should meet your standard as well, but no.  That's not the case.  Sorry, but whatever point you're trying to make has been lost in your inconsistencies. }

\textbf{inoffensive1}: \emph{I did not call this link news.  I referred to news sources as a context for the constant presence of bias-bashing, and the stupidity of it.  My belief has been that this link is essentially an op-ed published by the President, and should be recognized as such, but not disregarded on that account.}

\textbf{qmechan}: \emph{Okay. Homework done. You're wrong. Go me!}

\textbf{ArthurLaumann}: \emph{Wrong how?}

\textbf{qmechan}: \emph{Insert 1.99 for another minute of correction. Sorry.}

\textbf{ArthurLaumann}: \emph{What correction?}

\textbf{qmechan}: \emph{Operators are standing by.}

\textbf{ArthurLaumann}: \emph{Standing by what?}

\end{alltt}