\begin{alltt}
\normalfont
\textbf{100002475047373}: \emph{I want eeuu to enter default}

\textbf{100002541057840}: \emph{(Y)}

\textbf{100000099448491}: \emph{Need to stop this now and start America fresh}

\textbf{100000604568244}: \emph{They're big spoiled brats!}

\textbf{1448332271}: \emph{End it!}

\textbf{100000439344389}: \emph{In NJ vote for Cory Booker tomorrow.  The last thing we need is another sellfish republican}

\textbf{100001615644558}: \emph{Why aren't they all arrested and tried for treason}

\textbf{1815296962}: \emph{Impeach OBAMA and it will END!!!}

\textbf{1203909209}: \emph{Dem & rep all crooks & all need to go! End corporate america replace all politicians with school teachers}

\textbf{1344557634}: \emph{Without money maybe you can finally stop your useless and inhuman wars and start to care at your people mr President}

\textbf{1446489575}: \emph{There's nothing more annoying than a broke republican!!!}

\textbf{514223776}: \emph{Please Mr Obama is there anyway that you can force them to stop this shutdown. ..it's gone long enough. ..and we the poor will pay the price}

\textbf{632262577}: \emph{http://www.youtube.com/watch?v=cpoauPwY0rU&feature=player_embedded}

\textbf{1393291060}: \emph{They are kidding right....they are kidding me right.....ooohhhh it's about to get on and poppin....bring the economy shutdown.....see how well that goes w/u.....remember if the little ppl can't work...big ppl like Uhm the republicans won't get paid either.....we could do this all day.....when revolutionary starts evolutionary thats when things goin to get crazy.....then we destroy each other and that will b THE END......smh.....sad ending}

\textbf{1542871399}: \emph{Just because your side lost the election and you didn't get your way doesn't mean you teabaggers have to go all seditionist on us. America !  love it, or leave it.  Dont say you are a " patriot" if you can't even abide by the basic laws of this great country. The deficit is down more than 40%;  GDP is on the  upswing and the economy has improved. Funny all you " patriots"  were so quiet when Bush was driving us into the ditch.}

\textbf{1341223950}: \emph{Stay firm Mr. President !   God Bless !!!}

\textbf{802655642}: \emph{I just wish we would pass a budget that showed us removing our debt}

\textbf{100001214313621}: \emph{The Tea Party wants to default on our debt to prove to us all that they are in control ...they are ruining our country and everything we stand for}

\textbf{100000182147310}: \emph{Ill never vote again}

\textbf{668175153}: \emph{Private owners taking public resources for themselves are a political interest too. You don't have to have a political party name beside your name to have a political agenda.}

\textbf{100000816166660}: \emph{Dear mr obama,

                           your oppsition party want to prove u a week president.and people don't want a week leader.so my idol leader plese think some new.fro whole country.}

\textbf{1585221143}: \emph{Again there is no Bankruptcy court in the sky to bail us out is there and if we look how much we owe we are worth not much are we? So we are not the richest country in the world any more and that is all you guys fault. Really why don't all our reps let the people know how much they make> av &196,000.00 severance pay to make the fortune 500 envious, and some even if they die the wives get a pay check!!!! They can only make an extra $35,000.00 a year after pay but if they have a business or in the name of spouse or trust fund they can still get dividends, they can sell books and make as many speeches with ample pay. The many speeches and speaking engagements all for a price, and campaigning is imperative in the schedule and  than last but not least we the people. Maybe when people cause mayhem it feels better if the rest world is in mayhem with us have a free for all than people won't complain?}

\textbf{100006744933199}: \emph{Is the shutdown of america is due to nearness with iran & israel is anger for that & the whole economy of america is in hand of israel.so obama excuse with iran & give the happy to his step son istael.}

\textbf{100005327682497}: \emph{are billionaires get hurt every time this unproductive, congress has made the fight and hurt all americans to the turn of 3 trillion dollars all because they do not like a black president , we voted the numbers are in for over 8 years , and over runs and high cost to we the people all because of this pot smoking republican congre  !!!!}

\textbf{1545944548}: \emph{the house wants a bill where  prez and others r not exempt from obamacare, and  Obama says no.  So who r u going to blame for this}

\textbf{100000280675860}: \emph{Tea party republicans in Congress are a living, breathing, walking, talking argument for birth control.}

\textbf{1064820047}: \emph{Republicans....why y'all so selfish?!}

\textbf{100003504710492}: \emph{YES, stop the Madness!!!!}

\textbf{1636115397}: \emph{Those who vote democrap in next election will be signing a death warrant for this country. How much more can Americans take before it all crumbles? We need to get back to our morals and compassion for all Americans, we cannot do that with the current resident in the White House. Read this and maybe...just maybe you will begin to see the light.   http://www.foxnews.com/opinion/2013/10/10/mr-obama-presidency-is-no-place-for-amateurs/}

\textbf{758192074}: \emph{I told you so!}

\textbf{1377522722}: \emph{All of them should be fired}

\textbf{100000077125493}: \emph{GET RID OF ALL OF THESE " TEA PARTY BASTAEDS" Out of Congress........Start with them 2 (POS's......Boehnor and Cantor)}

\textbf{1354163800}: \emph{Isn't it [congres] already ended? Isn't that the point?}

\textbf{561778718}: \emph{More like kinda garden tea party carry on}

\textbf{1417541051}: \emph{they are the reason for everything that has gone wrong in american history. look it up. EVERY LAST BLUNDER BY A REPUBLICAN'T}

\textbf{224783034340255}: \emph{Ataturk did revolution ! building moderate muslim network is oxymoron which has been destroy secular , democratic, rule of law in Turkey. now our state is decayed , PM Erdoğan controls all state institutions. Mr. Obama , your  the great middle east project has turned into radical islamist in the middle east, especially in Syria , in Turkey. you don't have right to change regime of sovereignty states that is enthnocentricism led to fascism in the middle east. let's allow sovereignty nations act by themselves. You don't have right to stop Turkish enlightenment ! Atatürk established Turkish Republic, not George Washington. Turkey is ally with the NATO. but it doesn't mean Turkey is 52  city of the USA. we are independent nation that is Turkish nation. don't divide us ethnic, religious line , stop imperialism. Actually neo-liberalism is not only destroy foreign countries which the USA is selling it, it destroyed the USA economy. this fact was  indicated  few centuries ago by Immanuel Kant who said if state is getting bigger and bigger, it begins to lose, you cannot control whole states and nations. because people like freedom and independent , hate imperialism. think about  the US prestige around the world, nothing. so you don't have right to destroy American's honor, too. many American friends told me that we don't have power to stop the USA foreign policy. there is two political party, we just vote for it. therefore listen to ordinary peaceful people instead of brutal oil and weapons companies. thanks http://www.youtube.com/watch?v=ES-gd8CdUps}

\textbf{1268547410}: \emph{Can we DE-PORT them to Iran}

\textbf{1202881117}: \emph{END THIS NOW!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!}

\textbf{686665622}: \emph{https://www.facebook.com/photo.php?fbid=578369338867398&set=a.489104871127179.97989.475633619140971&type=1&relevant_count=1}

\textbf{100003814790567}: \emph{The best example of how utterly clueless the Republican rank and file are and what a shameless bunch of liars the Republican leadership is, is the fact that George Bush ran as a "political outsider" even though his father had been President, vice president and head of the CIA, his grandfather was a senator and career politician and his brother was governor of Florida.

How much more of an insider can anyone be?

At this point the Republican party simply lies out of habit. It's always worked for them in the past, why should they stop now?}

\textbf{100000203984762}: \emph{Truth, you want it? Republican anarchists have taken the rest of the republicans hostage too, they changed the house rules so that the majority of the republicans do not override the few republican anarchist who planned the government shutdown. the republican anarchists as of Oct 1,2013 changed house rule 22 clause 4 so that no other republican could reopen government. House rule 368 section 2 only allows the leader and his designee to reopen government, so in short words only the republican anarchist house leader can reopen government. Hmmmmmm, so they blame their brother for spilling the milk, but it is republican anarchist who are exercising tyranny.}

\textbf{538134987}: \emph{Dear....you all are like sheep to the slaughter and you don't even realize it.  Obama will literally strip you of everything you know so he can become dictator of what he thinks is going to be another 3rd world country.  It doesnt matter if you are democrat republican tea party liberalist......Obama dont care...he just wants you life.}

\textbf{1214268832}: \emph{Fitch Ratings has placed the United States on Rating Watch Negative on the high risk that US authorities will not raise the debt ceiling in a timely manner before the Treasury exhausts extraordinary measures on 17 Oct.}

\textbf{100001065167437}: \emph{Kill them now, impeach them now. The american people dont need masters}

\textbf{792805014}: \emph{this totally sucks!}

\textbf{100004617033907}: \emph{GOP brought down a country of 240 years of history in only 16 years, they spent 12.000.000.000.000 $ on those 16 years which is 75% of our current debt, and they have the stone face to blame the black president. You have to be very ignorant to actually believe them}

\textbf{1220771846}: \emph{End Obama NOW!}

\textbf{100003963291599}: \emph{Amen}

\textbf{1068817769}: \emph{http://dailycaller.com/2013/09/30/company-with-1-2-billion-obamacare-contract-under-investigation-for-serious-fraud/2/}

\textbf{1224048062}: \emph{Here’s a List of 313+ Employers Who Have Cut Hours Because of Obamacare 

Houston County
Biola University
Bealls Inc. (Department Stores)
SeaWorld Entertainment
Palmer Place Restaurant
Salina Family YMCA
Middletown Township Public Schools
Sam Houston State University
Auburn Hills
Friendship Community (group home for adults with disabilities)
Meridian Public Schools
Michael Monti’s La Casa Vieja steakhouse
Hollywood Casino
Arizona State University
Mainesubway (Subway franchisee)
Finger Lakes Community College
Tsunami Surf Shops
Southern Illinois University
Vincennes
Mexican American Opportunity Foundation
Georgia Military College
Vcm Inc. (Subway franchisee)
Ball State University
Tom’s River
Forsyth Technical Community College
Wilkes Community College
Consolidated Restaurant Operations Inc
Dave & Buster’s
Philadelphia University
K-VA-T Food Stores
Three Rivers College
Bergen Community College
University of Alabama
Brevard County
Buca di Beppo restaurant chain
Hillsborough Community College
St. Petersburg College
Cherokee County School Board
Hancock County
Morgan County
Central Michigan University
NEMF trucking company
Henderson
White Castle
Shari’s restaurants
Carnegie Museum
Oneida Special School District
Scott County School System
Stewart County School System
Jim’s Restaurants
Christoper Savvides restaurant & catering co.
Minocqua-Hazelhurst-Lake Tomahawk School District
Trig’s Supermarkets
University of North Alabama
Fatburger
Lee County
Delta County
Bee County
Boundary County
Rutherford County
Lawrence County
Kenowa Hills Public Schools
City of Burlington Public Schools
Lion & Rose British Restaurant and Pub
MTC Inc. restaurant management
Millard School District
Pulaski Technical College
San Diego Community College District
Drury University
Cumberland University
Area Agency on Aging of Western Arkansas, Inc.
Wal-Mart Stores Inc.
CKE Restaurants Inc.
Kern County
Rancho Cucamonga
San Gabriel
Palm Beach State College
Santa Fe College
Tallahassee Community College
Parkland College
Clay County
DeKalb County
Eastbrook Community Schools
Floyd County
Highland
Indiana University
Ivy Tech Community College
Kosciusko County
Lakeview Christian School
Madison Consolidated Schools
Madison-Grant United School Corp.
Marshall County
Mississinewa Community Schools
Perry Central School Corp.
Shelbyville Central School System
Speedway Schools
Starke County
Wolfe’s Auto Auction
Spencer Community School District
Lexington Board of Education
Howard Community College
Russ’ Restaurant
Maritz Research
Blair Community Schools
Plattsmouth Board of Education
Little Falls Board of Education
Lake Township
Lebanon City
Mason
Scrambler Marie’s Restaurants
Westlake
East Penn School District
Southern Lehigh School District
Tredyffrin-Easttown School District
Kelly Professional Cleaning Services
Spartanburg Community College
Matagorda County
Wilson County
Murray School District
Nebo School District
Henrico Country School District
Lynchburg
Clyde’s Restaurant Group
Eminence Community Schools
Faribault
Martin County
Baldwin Public Library
Hayfield Community Schools
Rappahannock Area Community Services Board
Benton Community Schools
Pompton Lakes Board of Education
Sparta Area Schools
Brandywine Heights Area School District
Southern Utah Unversity
Arkansas State University
Texas Christian University
Maricopa Community Colleges
University of Arizona in Tucson
Long Beach
Circle K Southeast
College of DuPage
McHenry County College
Eastern Hancock School Board
Fayette County School Corp.
Fort Wayne Community Schools
Gibson County
Greencastle Community Schools
Hancock Madison Shelby Educational Services
Tipton County
Vigo County School Corp.
White River Valley School District
Zionsville Community Schools
Indianola Community School District
Tama County
Kansas Turnpike Authority
Republic Foods (Burger King franchise operator)
Birmingham
Dearborn
Iosco County
Tuscola County
Douglas County West Community Schools
Papillion-La Vista school district
Westside Community Schools
Carlie C’s
Sinclair Community College
Tipp City
Ephrata Area School District
Dallas County Community College District
Plano
Alpine School District
Deseret Industries (work training for war refugees)
Wise County School Board
Mount Horeb Area School District
Tehama County
Crawford County
Vanderburgh County
Campbell County Social Services Dept.
Dickenson County Public Schools
Grayson County
Strasburg
Wythe County
North Putnam Community Schools
Northwestern School Corp.
Taylor Community Schools
Hanover Township
Middletown Township
Cedar City
Dallas School District
New Mexico State University
General McLane School District
Blue Ridge Community And Technical College
Fountain Fire Dept.
North of the River Recreation and Park District
Charco Broiler
Durango
Mountain Del (Del Taco franchisee)
Daytona State College
Moraine Valley Community College
Bartholomew County
Delaware County
Northwestern Consolidated School District
Richland-Bean Blossom Community School Corp.
Clear Lake School Board
Ocean City
Kalamazoo Valley Community College
St. Clair Community College
Moberly Area Community College
Ralston School District
Springfield Platteview Community Schools
Community College System of New Hampshire
Franklin Township Board of Education
Waldbaum’s Supermarket
Cuyahoga Community College
University of Akron
Upper Arlington City School District
Firstaff Nursing Services Inc.
Lancaster County School District
Penn Manor School District
Susquenita School District
Regal Entertainment Group
Brigham Young University
Chesterfield Public Schools
Chippewa County
Tazewell County
Eastern Greene Schools
Portage
Vassar Public Schools
Richmond Public Schools
Spotsylvania County
Joe Bologna’s Italian Pizzeria & Restaurant
Clinton-Glen Gardner School District
Elmhurst College
Columbus State Community College
AAA Parking
Boone Community School District
Joliet Junior College
Van Buren Township
Mankato
Hudson Valley Community College
Five Guys Burgers and Fries franchise
Akron
Baldwin-Wallace University
Kent State University
Lakeland Community College
Youngstown City Schools
Lori’s Angels home care
Granite School District
Chesterfield County
Louisa County
Bowling Green State University
Medina City Schools
Carnegie Library of Pittsburgh
Fairview Park
Shawnee State University
Miami Dade College
Putnam County
Cutchall Management restaurant company
Mount Ephraim Board of Education
CY Farms
Brunswick
Medina
Wytheville Town Council
Christopher Newport University
College of William & Mary
Norfolk State University
Virginia government (all other departments)
Virginia Commonwealth University
Virginia Community College System
Virginia Dept. of Alcoholic Beverage Control
Virginia Dept. of Conservation and Recreation
Virginia Employment Commission
Washington County
Wytheville
Land’s End
Dept. of Behavioral Health and Developmental Services
Dept. of Motor Vehicles
George Mason University
James Madison University
Longwood University
Old Dominion University
Radford University
University of Mary Washington
Lomira School District
Lancaster County
Utah Valley University
Columbus
Illinois Valley Community College
Milford Township
New Baltimore
Omega Foods Inc. (Wendy’s franchisee)
Tallmadge
Treadwell Enterprises (Taco Bell franchise operator)
Lake County
Boca Raton
Rock Valley College
Royal Farms convenience stores
Fairlawn
Chesapeake College
Sugarcreek Township
RREMC Restaurants (Denny’s franchisee)
Cedar Falls
Kga Group (Subway franchisee)
Kean University
Stark State College
Youngstown State University
Community College of Allegheny County
Pillar Hotels & Resorts
PMTD Restaurants LLC (a franchisee of KFC)
Jimmy John’s Gourmet Sandwiches
Plainfield Park District
Bowlmor Lanes
West Perry School District
Lafayette School Corp.

This isn’t just a list. This represents millions of lives damaged by an out of control president, congress, and Supreme Court. It’s time to fight back.}

\textbf{100000485887885}: \emph{I agree with Kate}

\textbf{100000140313752}: \emph{Amen!  This president is bankrupting our country, he is disrespectful to our troops and could care less about it!  Wise up people! He has it made for the rest of his life while we pay off the debts!}

\textbf{100005782921113}: \emph{I am speaking to you before it happens. I AM YOUR REAL PRESIDENT. I AM THE REASON WHY THE GOVERNMENT SHUTS DOWN LIKE MY SYSTEM BY THE BAK. I AM FROM SHENOUDA COUNTRY EGYPT, AND I LIVE IN CANADA. I ORDERED THE MAKING OF THE AMERICAN NEW BAK AS AMERICANS BECAME BAKS. I AM THE ONE. I AM THE MAN. I MADE YOU AND YOU ARE MINE. LEND ME A HELPING HAND SO THAT WE CAN MEET AND SPEAK, AND SO THAT I CAN LEAD.I AM TALKING TO YOU 2 DAYS FROM THE GLOBAL DISASTER AND AN AMERICAN RECESSION. ....}

\textbf{100001918863791}: \emph{Damn tea party........}

\textbf{100003145330402}: \emph{All you tea party sheep listen up. Educate yourself with facts not rhetoric. Go to your church & pray for your own racist anti black and anti Muslim souls !}

\textbf{100006115351513}: \emph{WE GO'N DIE}

\textbf{588078686}: \emph{How's that?}

\textbf{100001625032824}: \emph{Stay strong!  Don't negotiate with terrorists}

\textbf{622475051}: \emph{Welcome to Big Brotha's Amerika!

Washington (AFP) - The National Security Agency is gathering email and instant messenger contact lists from hundreds of millions of ordinary citizens worldwide, many of them Americans, The Washington Post reported late Monday.

http://news.yahoo.com/nsa-gathering-millions-email-address-books-022258955.html}

\textbf{100002896021307}: \emph{What makes them so special that they cant be on obamacare..they are employees of the american people who are being forced on it..if I am there employer why does my employee deserve better special insurance}

\textbf{100002896021307}: \emph{You say there insurance is government funded..the government is broke..looking to raise the dept ceiling..so who is paying for the goverments platinum insurance?..me and the rest of america..I also didnt approve of that..does the government just do what it pleases without asking there employer's..you know the american people}

\textbf{100000248123927}: \emph{http://buff.ly/H26XL6, lol phuck off and dye obama.}

\textbf{100002896021307}: \emph{Still would like to know the answer to why obama and the rest of dc isnt the first to be on obamacare..its great as obama says ..but hes never going to put his family on his wonderful legacy..why is that}

\textbf{1297265231}: \emph{Affordable care act is the wrongly named, it's not affordable at all}

\textbf{1340351093}: \emph{is this all we can do just sit around and rant and rave}

\textbf{691484965}: \emph{Yes Obama, Heath and his small dog & tv have your back, never mind the millions on pissed off hard working Americans who embrace the their second amendment right to fight against your tyranny}

\textbf{588078686}: \emph{Facebook is such a solid reference.}

\textbf{100000598223919}: \emph{https://scontent-b-iad.xx.fbcdn.net/hphotos-prn2/1374238_10151804141372740_429618168_n.jpg}

\textbf{100001371634460}: \emph{Slavery was supported by democrats and upheld by the supreme court so are we says just bc Obamadontcare is law all laws are good? Or are some worth fighting against}

\textbf{1064649604}: \emph{randy... do u like obamacare or do u live off the government???}

\textbf{100004617033907}: \emph{I love when they cry my name!  Proves they can't prove me wrong and that the truth hurts them!  LOL}

\textbf{1297265231}: \emph{The democrat party is for brainwashed people and the republican party is for extremely dumb people... the third party, independent tea party/libertarian party are for people that think for themselves and are capable of critical thinking}

\textbf{100001446622812}: \emph{isnt obamacare putting 800,000 at work....then it must go on....but if there are problems, then we must be flexible...every great project has hiccups in the beginning,....then again.....16 trillion in debt means health is the first to go....and that is a republican debt not a democrat debt....thank you and god bless....:)}

\textbf{100000313051307}: \emph{Doing such things shows that they DO NOT LOVE THEIR COUNTRY & THE COUNTRY PEOPLE because it is not the president who is affected it is the COUNTRY & PEOPLE. So the countrymen should realize and in the NEXT ELECTION be RATIONAL and see that they do not have place for SUCH GROUPS... Iam not an American Citizen but I felt that what is the TRUTH must be written .}

\textbf{100000048412359}: \emph{Obama is incapable of telling the truth.  What a coward.}

\textbf{1387836445}: \emph{Credit rating IS going down because of out of control spending, and you acting like a child..  unwilling to make even the smallest concession in your SPENDING TRILLION$ of $$$$ of --OUR MONEY--.}

\textbf{100002812420842}: \emph{There is no god but Allah}

\textbf{1665312220}: \emph{SHUT THEM DOWN!!! Every person in this country should be on the streets with signs in their windows, lawns and cars to SHUT DOWN THE GOP!!!!!}

\textbf{100002786795376}: \emph{jajajajajajajaajajjajajaj http://www.youtube.com/watch?v=nlaTY9hQAlo}

\textbf{100004509844910}: \emph{f&am.}

\textbf{804422261}: \emph{Tea Party Republicans? The Senate was given an offer that gave you what you wanted and the Senate refuses it, then it is the Democrats that are holding America hostage. I blame Obama and the Democrats.  And If You Democrats can paid officers to keep something closed, then you can keep it open...you liberals are just retarded! And the debt ceiling, why raise it? that is only giving a credit card more credit to spend money America don't have...And you Liberals are out right lying when you say America will default, Washington takes in approx $225 billion a month, you must pay the debt which is approx. 30 Billion a month, the only way America will default is if President Obama refuses to pay it, will he go against the Constitution? STOP scaring the American people!}

\textbf{1609012664}: \emph{I think it is time for Obama to use the power of his executive office to open the government and raise the debt ceiling per his constitutional right of cause. The TP GOP want him to fail even if they bring down the whole country to achieve it. In response to Russell, keep assuming its Obama's fault, regardless how many times you and the GOP repeat that line, it will never change the fact that the shutdown was caused by GOPs in House of Representative. Its now in the History books.}

\textbf{100004457379547}: \emph{vote 4 demo its the only way or the highway}

\textbf{100000873044575}: \emph{Guess Ted Cruz dosen,t like his job, Vote him out}

\textbf{1378523519}: \emph{For real  Nick Dippold!}

\textbf{100001214723824}: \emph{Does anyone understand who or what the tea party is and how they have become so powerful?}

\textbf{1446593804}: \emph{still think its the tea party or the republicans that is wreaking havoc on our way of life.  

100 Percent FED Up

BEST VIDEO EVER!!!! FANTASTIC SUMMARY OF THE DEBT CRISIS FROM REP. TOM MCCLINTOCK.....PLEASE SHARE!!!
#REPTOMMCCLINTOCK 
https://www.youtube.com/watch?v=QV8NcbbGCZY

The Debt Crisis 
www.youtube.com
October 14, 2013.}

\textbf{1235944006}: \emph{Squealing Pig Obama democrats AND Junk Liberal Media keep howling Obamacare is the law and we should accept it and move on. I say; 1-It was passed illegally and late on a Friday night hoping we would NOT notice. 2-Obama democrats EXEMPT themselves from it Totally because they do NOT want the bad sides of it themselves. 3- BO's exemptions and regulations-all UNconstitutional-since the ACT passed are THREE times the length in paperwork of the Illegal law itself. 4-Obamacare was approved by the supreme court by ONE vote, Justice Roberts who has 3 illegally adopted children and was flat out Black Mailed by Obama people with the threat of having his children removed from his life and Roberts being REMOVED from the Supreme Court if he did not vote FOR Obamacare with nonsense claims about the legality of it. Defund ObamaCare! 5-BOcare includes post birth abortion/murder of babies if parents do NOT like anything about them.}

\textbf{1227712350}: \emph{Who do you think knows more about the Constitution? You or someone who was considered a Constitutional scholar and TAUGHT the Constitution?}

\textbf{680285848}: \emph{Get rid of the tea party!}

\end{alltt}