\begin{alltt}\normalfont\textbf{Apologianick}: \emph{@BarackObama I thought a president was supposed to lead...}

\textbf{ItsChris96}: \emph{@BarackObama FOLLOW ME AND ILL REOPEN THE GOVERNMENT}

\textbf{salyvi}: \emph{@thetropico @BarackObama YOU ARE A HORRIBLE PERSON !!  Racist pig!}

\textbf{GSorensen}: \emph{@BarackObama Stop expanding government, spying on Americans and driving up the deficit.}

\textbf{DemsAbroad}: \emph{RT @BarackObama: This is unacceptable. Tell Tea Party Republicans to stop holding our economy hostage: http://t.co/7pD7lA7ZSA}

\textbf{kade6767}: \emph{@Apologianick The president can only so much when idiot republicans refuse to do their jobs properly @BarackObama}

\textbf{Apologianick}: \emph{@kade6767 @BarackObama all presidents must work with Congress. Every budget they've submitted has been turned down.}

\textbf{kade6767}: \emph{@Apologianick Because they have not been clean bills. The president wants a clean bill. That IS doing his job}

\textbf{kade6767}: \emph{@Apologianick Uh, do you not really follow politics or government or even understand it at all? Seriously? Are you learning disabled?}

\textbf{Flandrin78}: \emph{@kade6767 @Apologianick So, because the budget doesn't contain exactly what He wants, Almighty O refuses to fulfill his fiduciary duties?}

\textbf{Apologianick}: \emph{@kade6767 I just expect you to back a claim. Must be hard.}

\textbf{kade6767}: \emph{@Flandrin78 He has no duty to accept unclean bills.}

\textbf{Flandrin78}: \emph{@kade6767 @Apologianick ?..continued... That is completely irresponsible.}

\textbf{kade6767}: \emph{@Apologianick Back a claim? It's not a claim, it's fact. There's the problem with you repubs, too stupid to learn shit on your own}

\textbf{Apologianick}: \emph{@kade6767 when argument fails, ad hominem!}

\textbf{kade6767}: \emph{@Flandrin78 Irresponsible to do his job? Ok, do you not live in the USA or have any clue what a president can and can't do?}

\textbf{kade6767}: \emph{@Apologianick I have no time for fucking morons like you. Follow what the fuck is happening in the country, don't fucking ask for help}

\textbf{kade6767}: \emph{@Apologianick It's your job to fucking pay attention I don't need to do that for you idiot}

\textbf{Tea4gunsSC}: \emph{@BarackObama Mr President u are holding America hostage.}

\textbf{Tea4gunsSC}: \emph{@kade6767 @Apologianick @BarackObama The idiots are those who refuse to talk---u know who u are--if the shoe fits wear it}

\textbf{DelMel_2}: \emph{@Tequilablessed @keshasbestmate @BarackObama very distasteful}

\textbf{theblindsword}: \emph{@Flandrin78 if you believe you're a complete idiot.}

\textbf{Tea4gunsSC}: \emph{@kade6767 How do u think name calling and profanity make u sound or appear to have any intellect}

\textbf{Flandrin78}: \emph{@theblindsword If I said to you that your beliefs make you a complete idiot, what would you say?  Is that any way to constructively argue?}

\textbf{Flandrin78}: \emph{@theblindsword Why don't you come back with your opinion on why you think I am wrong.}

\textbf{kade6767}: \emph{@parisreeves66 That's on the employer as I said. Fear mongering. Blame those employers NOT the ACA}

\textbf{kade6767}: \emph{@parisreeves66 And you'd rather pay higher insurance premiums and pay for the uninsured? That's acceptable to YOU?}

\textbf{kade6767}: \emph{@CMMSJ I mean, don't make comments without understanding what congress does ya know? I know, it's crazy and they always want help}

\textbf{kade6767}: \emph{@CMMSJ because they don't know where to find the info themselves}

\textbf{kade6767}: \emph{@Tea4gunsSC Fuck off cunt}

\textbf{axomamma}: \emph{@Flandrin78 @rakilee @BarackObama You are mistaken. Go look at the numbers.}

\textbf{kade6767}: \emph{@CMMSJ lol, I know I start calling them idiots because at that point it's useless to argue with them, they've won with their experience}

\textbf{kade6767}: \emph{@parisreeves66 I did not say ACA has to end and it was done right. Kinks will be worked out.}

\textbf{Flandrin78}: \emph{@axomamma @rakilee @BarackObama If you know the numbers, then please tell me how many Dems lost their seat the last two rounds?}

\textbf{kade6767}: \emph{@CMMSJ And a big problem is everyone hearing so many untrue facts and they believe everything. Just read the bill. So simple.}

\textbf{BaruckObuma}: \emph{. @BarackObama http://t.co/N6w3jwhO5h}

\textbf{kade6767}: \emph{@CMMSJ lol, right ? They don't get that if everyone has access to affordable healthcare then everyone pays their fair share}

\textbf{stfu_v}: \emph{“@BarackObama: This is unacceptable. Tell Tea Party Republicans to stop holding our economy hostage: http://t.co/6Nd23jxtPu” 

Brainwasher}

\textbf{kade6767}: \emph{@CMMSJ They also don't get if they pay for insurance now, part of out premiums go toward paying for ER visits and the uninsured}

\textbf{stfu_v}: \emph{@CMMSJ @BarackObama OMG stfu}

\textbf{kade6767}: \emph{@CMMSJ Hope you have a great night. I think I am all politically talked out for the night lol, I need to finish some work 😊}

\textbf{clownbabyy}: \emph{@kade6767 @CMMSJ he asked you what was unclean about the bills and you completely dodged the question, don't act like the higher power bud.}

\textbf{Jennster81}: \emph{@Flandrin78 @BarackObama are you drunk Jeremy? I wouldn't want a tea bagger representing me EVER.}

\textbf{Flandrin78}: \emph{@Jennster81 @BarackObama And I didn't want a Lib ever, but society at that time willed it.  Times and majority views are changing though :)}

\textbf{kade6767}: \emph{@clownbabyy I'm not your civics teacher. Try being smart enough to learn on your own. This one is not hard. Unless you're an idiot.}

\textbf{Tequilablessed}: \emph{@tornari117 @CMMSJ @keshasbestmate @BarackObama you don't either!' Stop blaming Him for your mishaps in life,,}

\textbf{kade6767}: \emph{@CMMSJ They don't understand the terminology. Clean bill: only the subject at hand addressed with nothing else attached @clownbabyy}

\textbf{clownbabyy}: \emph{@kade6767 then why didn't you enlighten him on what was wrong with the bills? You follow politics so much surely you could tell him before}

\textbf{clownbabyy}: \emph{@kade6767 resorting to childish acts such as using ad hominems (though this clearly wasn't the case)}

\textbf{clownbabyy}: \emph{@kade6767 I never implied you were my civics teacher and I never asked you to pass knowledge unto me, surely you meant to direct this to him}

\textbf{clownbabyy}: \emph{@CMMSJ you are forgiven, and you did not, in fact you were quite polite in your response.}

\textbf{nonoyawns}: \emph{@kade6767 @Apologianick Is this the part where the Obama apologist starts using insults that demean people with disabilities...? #fail}

\textbf{pbow40}: \emph{@BarackObama follow me off the cliff.}

\textbf{clownbabyy}: \emph{@CMMSJ their views is in question and it turns into a name calling shitstorm, ridiculous.}

\textbf{clownbabyy}: \emph{@CMMSJ well, being constitutionally conservative I believe that when a bill is passed through congress it is a law, the bill was deemed}

\textbf{clownbabyy}: \emph{@CMMSJ I thank you, have a good night!}

\textbf{clownbabyy}: \emph{@CMMSJ thank you soooo much for saying that, that's honestly what I aim for, do keep in mind that I am a dumb teenager though:p}

\textbf{BruessT}: \emph{@BarackObama obamacare is a joke, #united socialist states of america}

\textbf{RedScareBot}: \emph{Socialism lite RT @bruesst: @BarackObama obamacare is a joke, #united socialist states of america}

\textbf{troy0950}: \emph{@kade6767 @Apologianick don't forget the racist part, libtard fallback argument}

\textbf{troy0950}: \emph{@BarackObama don't think so u constitution hating communist}

\textbf{CodyAustin316}: \emph{@BarackObama goodbye freedom, hello socialism. I hope and pray you get impeached.}

\textbf{Dusty_Cole}: \emph{Same logic goes to them, Congress must work w/the Pres just as the Pres must w/them. #Reflexive @Apologianick @kade6767 @BarackObama}

\textbf{RedScareBot}: \emph{Globlist Agenda RT @codyaustin316: @BarackObama goodbye freedom, hello socialism. I hope and pray you get impeached.}

\textbf{kade6767}: \emph{@clownbabyy I don't have a law to follow here as to what I feel like saying, learn to educate yourself not have someone else do it for you}

\textbf{kade6767}: \emph{@nonoyawns That would be republicans that do that you clearly have that backwards}

\textbf{kade6767}: \emph{@StreetForensics One, read what I wrote and two the ACA is only a nightmare if you believe that's what Fox News told you}

\textbf{clownbabyy}: \emph{@kade6767 again I'm not asking you to educate me}

\textbf{kade6767}: \emph{@troy0950 Unless you have something intelligent to add, which of course being a republican you don't, go cry to someone else}

\textbf{kade6767}: \emph{@Dusty_Cole But a president can't make policy or force anything so that is why a president has veto power}

\textbf{kade6767}: \emph{@clownbabyy I'm talking about the other person and I am done with this useless conversation}

\textbf{troy0950}: \emph{@kade6767 not a repub, libtard. You 1st, what was ur word? Oh yea, motherfucker.}

\textbf{kade6767}: \emph{@troy0950 Go get yourself fucking educated you stupid cunt.}

\textbf{kade6767}: \emph{@troy0950 Some of you fucks need a good ass whipping. Please come to Miami, I'll be here til next month idiot}

\textbf{troy0950}: \emph{@kade6767 oh THAT was intelligent! You libtards have such a way with words}

\textbf{troy0950}: \emph{@kade6767 bring it bitch}

\textbf{clownbabyy}: \emph{@kade6767 why}

\textbf{hale_razor}: \emph{@BarackObama Interesting you repeat this "hostage" attack the same day Democrat Filner pleads guilty to false imprisonment.}

\textbf{troy0950}: \emph{@kade6767 blocked me &amp; ran away like the little libtard bitch u are lol}

\textbf{RedScareBot}: \emph{Fools On The Hill RT @georgiapopulist: @tornari117 @BarackObama you wouldn't know socialism if it hit you on the head}

\textbf{kade6767}: \emph{@Gmccormick6 Because they are the ones doing it out of fear not BECAUSE of the ACA, they started doing that the moment it passed}

\textbf{StaceyCripe}: \emph{@BarackObama Dear Dictator Obama, the House is merely exercising their constitutional rights. Try it sometime. http://t.co/LhwbWyjjoj}

\textbf{StaceyCripe}: \emph{@kade6767 @Apologianick @BarackObama They are doing their job. Try reading the Constitution sometime. http://t.co/wd6tGjfmYp}

\textbf{theblindsword}: \emph{@Flandrin78 if they're wrong, then yes.}

\textbf{theblindsword}: \emph{@Flandrin78 the shutdown was orchestrated by the gop. They even changed the rules on how to fix a shutdown on the same day they started it}

\textbf{kade6767}: \emph{@StaceyCripe Congress voted on it. It passed. The SCOTUS upheld it. Obama campaigned on it. GOP doesn't get to complain any further}

\textbf{dj1i}: \emph{@theblindsword @Flandrin78 Tea party are doing what they promised their constituents}

\textbf{theblindsword}: \emph{@dj1i @Flandrin78 them and the republicans have been talking about doing this since 2010.}

\textbf{dj1i}: \emph{@theblindsword @Flandrin78 Supreme Court was supposed to overturn it but didn't}

\textbf{theblindsword}: \emph{@dj1i @Flandrin78 because republicans changed the rules on who can turn over a shutdown.}

\end{alltt}